Draft

### 2016-09-03 Draft/draft.tex
1. Seperate the old note "Lectures on the Frontiers of Physics" from general    "Draft". Archive it inside the "Finished". 2. Initial commit to MH Wong's dissertation.

\section{Lectures on the Frontiers of Physics}
\textbf{Given by professor of physics in SUSTC}
    \subsection{By JQ. He.}
    \textbf{Thermal electrics}

    \subsection{By Lang. Chen}
    \label{sec:c.l}
    Grow thin films.
    \begin{itemize}
	\item Rheed-Assited PLD/MBE. (Ray as an exmination).
	\item 
	orbital contral of electrons -> 
	orbitronics -> Control of Spin orbital coupling.
	\item
	Multiferroics -> multiple order parameters, and the interaction
	between them. E.g. $BiFeO_3$.
	\item
	Ferrotorodicity: Spontaneous Toroidal Momennt. Time and spacial
	symmetries simultaneous broken.
	\item
	What is a iridates $Ir_2(X)O_4$, (e.g. $Sr_2RuO_4$) 
	exactly in theoretical physics?
	\item
	$H_2S$: 200K superconductor?
	\item
	The Double Exchange effect of oxygem -> Half-metal, phase transition.
    \end{itemize}

    \subsection{By Alan}
    \textbf{Photocatalysis}: $TiO_2$. Hongkong has $TiO_2$ spurred on
    the keys.

    \subsection{By Li, Huang}
    \begin{itemize}
            \item Computational Physics
            \item Surface Dynamics
            \item Structural factor from 2D to 3D.
            \item Finding Order Amid the Chaos. amorphous -> spatially
                    resolved distributed function.
            \item ?: What is genetically algorithm.
    \end{itemize}
    \textbf{Computational and theoretical studies of Surface dynamics}

    \begin{itemize}
            \item Surface atoms is immersed in a very different environment
                    compared with the bulk atoms.
            \item First-principle calculations
            \item DFT + LDA -> Conser equation
            \item Plane wave basis + Ultrasoft pseudopotentials to solve the
                    Conser equation
            \item Continumm method ?
    \end{itemize}

    \subsection{By Junfen, Liu}
    \begin{itemize}
            \item electronic transport in mesoscopic systems:
            \item Spintronics
            \item Graphene eletronics
            \item Superconductors etc.
    \end{itemize}
    \textbf{Quantum wire conductiing}
    The conduction channel in quantum wire is quantized, with discrete value
    of conductance.
    \begin{itemize}
            \item $\lambda_F$ Fermi wavelength
            \item $L_m$ Momuntum relaxation length <-- impurities.
            \item $L_\phi$ Phase relaxation length <-- memory of phase,
                    related to energy $\omega = E/\hbar$.
            \item $L$ Sample length
    \end{itemize}
    \begin{itemize}
            \item Ballistic transport: $L << L_m$ No scattering.
            \item Diffusive $L>L_m$, scattering, reduced transmission.
            \item Localization $L_m<<L<<L_\phi$ -> Prof. Haizhou Lu.
            \item Classical. (Omitted)
    \end{itemize}
    \textbf{Conductance}
    No back-scattering $$ G = \frac{I}{V} = \frac{2e^2}{h}$$
    Landauer formula $G = \frac{2e^2}{h}\cdot T$, $T$ is some coefficient
    accounting for the back scattering, perhaps the transmission
    probability.
    In reality, $G=\sum_{\text{Different channels}}G_i$,

    We can turn the $G$ into resisivity: 
    $$\text{Resistance}= \frac{h}{2e^2} + \frac{h}{2*e^2}\frac{R}{T}$$
    $R+T=1$

    \paragraph{Resonate Transmission} (Omitted)

    \paragraph{Spintronics} Use the extra freedom of Spin.

    Spin field eletroncis: Datta and Das, Appl. Phys. Lett. 56, 665(1990)

    GMR: 2007 Nobel prize in Physics.

    Hall Effect (Omitted)
    Spin Hall Effect: S. murakami, et.al. Science 301 1348(2004);

    J. Sinova et.al. Phys.Rev.Lett. 92, 126603 (2004). (Omitted)

    \paragraph{Graphene} Carrier -> Relativistic Dirac fermions.
    \textbf{Klein Paradox}

    \paragraph{Josephson Junction} A phase difference could conduct
    electricity in Superconductors.

    \subsection{By Haizhou, Lu}
    \paragraph{Quantum Anomalous Hall Effect}
    Requires strong magnetic field: $\approx 10$ Tesla.

    Anomalous Hall Effect: Without magnetic field. $R_H = R_0 B+ R_A M$
    where $M$ is the magnetic susceptibility.
    Two-factors: SO coupling. Spin-dependent Hall Effect.

    An excellent illustrations is found in \cite{Arxiv-Xiao}:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/1}
        \caption{Illustration}
        \label{fig:Xiao Illustration}
    \end{figure}

    \subsection{By Kedong Wang}
    Tunneling current $I\propto V e^{-2kz}$, where 
    $k = \frac{\sqrt{2m\phi}}{\hbar}$, $\phi$ is the Work function.
    $I$ is very sensitive to the distance $z$.

    \paragraph{Work function} $\phi$ characterize the obstruction
    that prevents electron from escaping the sample.

    \subsection{By Mingyuan Hunag}
    Not insterested.

    \subsection{By Wenkang Wong}
    \paragraph{Non-clone Theorem} We can easily see that there is no universal
    copy operators in Quantum Mechanics.

    \begin{proof}
    We proove it by contradiction. Let $U$ be the copy operator. By definition,
    we have
    $$   U \ket{\psi}\ket{0} = \ket{\psi}\ket{\psi}$$
    For any $\ket{\psi}$.
    Then, let try copying the state $\ket{\psi} = \ket{0} + \ket{1}$. We have
    \begin{align*}
        (\ket{0}+\ket{1})(\ket{0}+\ket{1}) &= U (\ket{0}+\ket{1})\ket{0} \\
        &= U (\ket{0}\ket{0} + \ket{1}\ket{0} ) \\
        &= \ket{0}\ket{0} + \ket{1}\ket{1} \\
    \end{align*}
    This is a contradiction.
    \end{proof}
    \begin{remark}
        We assume that the copyer is universal. This might seems to be too
        strong. However, if we assume that the copyer only
        works for certain states $\ket{\phi}$, then with the knowledge
        of these certain states, we could in principle create an exact copy
        of these states. This copy ,in the sense of another instance of the
        same object, of original state should not be considered to be an
        copied version of the original state.
    \end{remark}

    \subsection{By Liyuan Zhang}
    Not insterested.
\section{Problems in Bernevig's Topological ...}

@@

    \bibitem{DETA} Martin Braun. Differential Equations and Their
    Applications. 4ed. Springer.
    \bibitem{Arxiv-Xiao} \url{http://arxiv.org/abs/1508.07106v1}
    \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)
\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

>>>>

\section{Problems in Bernevig's Topological ...}

@@

    \bibitem{DETA} Martin Braun. Differential Equations and Their
    Applications. 4ed. Springer.
    \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)
\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
